Highlighting Disputed Claims on the Web

### 2009-10-30 papers/www_disputefinder/disputefinder.tex
Folded in changes suggested by Wes

Dispute Finder consists of a server-side database and a Firefox browser extension. The database contains a set of known disputed claims that appear on the web. For each claim, the database contains references to articles on the web that support or oppose it, and hints about how to recognize that disputed claim on the web (Figure~\ref{snippet_claim_article}). The browser extension maintains its own local copy of the database, and runs a textual entailment algorithm on every sentence the user views to determine whether it is likely to be making a known disputed claim.

@@

These findings were backed up by our interviews. Several participants told us that they regularly get information from sources that they do not entirely trust. A user might read information from an untrusted source because the source is interesting, entertaining, linked to from somewhere else, or it came up in a search. For example they might read Michael Moore because he is entertaining, or read articles mailed to them by friends.

@@

Unlike these annotation tools Dispute Finder does not allow a user to directly express their own opinions about a topic. Instead, the only way they can add or promote an opinion is to link to an article from a trusted source that argues for that opinion. Our interviews lead us to believe that most users would rather know the cases where a trusted source disagrees with what is being written, rather than when an unknown user disagrees.

Another key difference between prior annotation tools and Dispute Finder is that prior annotation tools allow a user to annotate {\it text on a page} while Dispute Finder attempts to allow a user to annotate a {\it claim} everywhere it appears on the web. If a user of an annotation tool adds an annotation to a page then their annotation will only appear on that page. If a user of Dispute Finder tells Dispute Finder to highlight a disputed claim, that claim will be highlighted on every web page on which Dispute Finder's algorithms determine that the claim appears. The closest annotation system to Dispute Finder is perhaps SparTag.us~\cite{Hong2009}, which uses an SHA hash to attach an annotation to an exact paragraph, irrespective of where it appears on the web; however a claim may be written in many different ways, and be part of many different paragraphs.

@@

The intention behind these tools is that a user uses them to identify the source of information that is being used to motivate a conclusion. These tools allow a user to mark up the facts made by a single document, but do not provide facilities for a user to mark up large numbers of documents as being the same claim.

@@

\subsection{Detecting Disputed Claims}

To highlight disputed snippets on a web page, Dispute Finder needs to identify which snippets are making known disputed claims. Our current implementation runs a simple textual entailment algorithm inside the browser to look for sentences that entail known disputed claims.

We implemented and tested four different approaches:

@@

\item[Client-side entailment:] The browser extension runs a simple textual entailment algorithm over all sentences on every web page the user browses, checking to see if any sentence on the page entails any claim in the database (Figure~\ref{nlp_client_server}). A user can enter additional paraphrases of a claim to help the entailment algorithm (Figure~\ref{paraphrases}). This is the implementation used by the currently released version of Dispute Finder.
\end{description}

@@

@@

\section{Evaluation}

>>>>

Dispute Finder consists of a server-side database and a Firefox browser extension. The database contains a set of known disputed claims that appear on the web. A disputed claim is a statement about the world that some people disagree with. For example ``global warming is a hoax'', ``gun control will reduce crime'', ``eskimos have many words for snow'', or ``margarine is healthier than butter''. A claim can be stated in many ways. For example ``margarine is healthier than butter'' and ``butter is worse for you than margarine'' are paraphrases of the same claim. For each claim, the database contains references to articles on the web that support or oppose it, and hints about how to recognize that disputed claim on the web (Figure~\ref{snippet_claim_article}).

The browser extension maintains its own local copy of the database, and scans the text on the current page for text snippets that appear to {\it entail} a claim. A snippet is a continuous region of text on a web page. A snippet is defined to entail a claim if a normal user reading that snippet would reasonably conclude that the author of the page believed the claim was true. For example ``the english have as many words for rain as the eskimos have for snow'' {\it entails} ``eskimos have many words for snow'', even though this claim is never stated explicitly.

@@

These findings were backed up by our interviews (Section~\ref{sec:interviews}). Several participants told us that they regularly get information from sources that they do not entirely trust. A user might read information from an untrusted source because the source is interesting, entertaining, linked to from somewhere else, or it came up in a search. For example they might read Michael Moore because he is entertaining, or read articles mailed to them by friends.

@@

Rather than allowing a user to directly express their own opinions about a topic, Dispute Finder instead requires a user who wants to promote a particular opinion to do so by linking to an article from a trusted source that argues for that opinion. Our interviews (Section~\ref{sec:interviews}) lead us to believe that most users would rather know the cases where a trusted source disagrees with what is being written, rather than when an unknown user disagrees.

Another key difference between prior annotation tools and Dispute Finder is that prior annotation tools allow a user to annotate {\it text on a particular page} while Dispute Finder attempts to allow a user to annotate a {\it general claim, everywhere it appears on the web, however it is worded}. If a user of an annotation tool adds an annotation to a page then their annotation will only appear on that page. If a user of Dispute Finder tells Dispute Finder to highlight a disputed claim, that claim will be highlighted on every web page on which Dispute Finder's algorithms determine that the claim appears. The closest annotation system to Dispute Finder is perhaps SparTag.us~\cite{Hong2009}, which uses an SHA hash to attach an annotation to an exact paragraph, irrespective of where it appears on the web; however a claim may be written in many different ways, and be part of many different paragraphs.

@@

These tools allow a user to mark up the facts made by a single document, but do not provide facilities for a user to mark up large numbers of documents as being the same claim, or to automatically inform a user when other sources disagree with what they are reading.

@@

\subsection{Detecting Known Disputed Claims}

To highlight disputed snippets on a web page, Dispute Finder needs to be able to determine when a snippet entails the truth of a known disputed claim. This is complicated by the fact that a claim can be phrased many different ways, and a snippet does not need to explicitly state a claim in order to entail its truth. For example ``I prefer margarine to butter because it is healthier'' entails ``margarine is healthier than butter''. Our implementation maintains a local copy of our claim database inside the browser extension and runs a simple textual entailment algorithm inside the browser to look for sentences that appear to entail known disputed claims.

There is a trade-off between precision and recall. We want to maximize the likelihood that Dispute Finder will highlight a snippet if it is making a known disputed claim, while minimizing the likelihood that it will highlight a snippet that is not making a known disputed claim.

We implemented and tested four different approaches that represent different points along this trade-off:

@@

\item[Client-side entailment:] The browser extension runs a simple textual entailment algorithm over all sentences on every web page the user browses, checking to see if any sentence on the page entails any claim in the database (Figure~\ref{nlp_client_server}). A user can enter additional paraphrases of a claim to help the entailment algorithm (Figure~\ref{paraphrases}). This is the implementation used by the released version of Dispute Finder.
\end{description}

@@

\subsubsection{Textual Entailment}

@@

\section{Evaluation}
\label{sec:interviews}
